---
title: 'Chapter 3: Attribute data operations'
author: "Yifei Liu"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(sf)
library(raster)
library(dplyr)
library(ggthemes)
library(rcartocolor)
library(stringr) # for working with strings (pattern matching)
library(tidyr) # for unite() and separate()
library(spData)

```

## 3.1 Introduction

For vector data, sf dataset, this means operations such as subsetting and aggregation. 

For Raster attributed data operations cover creating continuous and categorical raster alyers and extracting cell values from one layer and mltiple layers 


## 3.2 Vector attibute manupulation

```{r}
methods(class = "sf")

```

```{r}

dim(world)
nrow(world)
ncol(world)

# remove its geometry

world_df <- st_drop_geometry(world)
class(world_df)

```

### 3.2.1 Vector attibuted subsetting

### 3.2.2 Vector attibute aggregation

```{r}

aggregate(pop ~ continent, FUN = sum, data = world, na.rm = T)
aggregate(world["pop"], by = list(world$continent),
          FUN = sum, na.rm = T)


```


### 3.2.3 Vector attribute joining

use dplyr _join() functions

```{r}
world_coffee <- left_join(world, coffee_data)

class(world_coffee)

ggplot(world_coffee) +
  geom_sf(aes(fill = coffee_production_2016)) +
  scale_fill_gradientn(colors = carto_pal(name = "TealRose", n = 7), na.value = NA) +
  theme_void() +
  theme(legend.position = "none")

```


```{r}

setdiff(coffee_data$name_long, world$name_long)



```

### 3.2.4 Creating attributes and removing spatial information

## 3.3 Manipulating raster objects

```{r}

elev <- raster(nrows = 6, ncols = 6, res = 0.5,
               xmn = -1.5, xmx = 1.5, ymn = -1.5, ymx = 1.5, 
               vals = 1:36)

plot(elev)
```

```{r}

grain_order = c("clay", "silt", "sand")
grain_char <- sample(grain_order, 36, replace = T)
grain_fact <- factor(grain_char, levels = grain_order)

levels(grain)[[1]] <- cbind(levels(grain)[[1]], wetness = c("wet", "moist", "dry"))

levels(grain)
factorValues(grain, grain[c(1, 11, 35)])

plot(grain)

```

### 3.3.1 Raster subsetting

Raster subsetting is done with the abse R operator [, which accpets a varity of inputs:

- Row-column indexing
- cell IDs
- Coordiante
- Another spatial object

```{r}
elev[1,] # row1, column1
elev[1] #cell ID 1

```

For multi-layered raster objects stack or brick, this will return the cell values for each layers. 

```{r}
r_stack = stack(elev, grain)
names(r_stack) = c("elev", "grain")

# three ways to extrac a layer of a stack

raster::subset(r_stack, "grain")
r_stack[["elev"]]
r_stack$elev

```

cell values can be modified by overwrting existing values 

### 3.3.1 Summarizing raster objects

```{r}

# RasterLayer
cellStats(elev, sd)
# Raster*

summary(brick(elev, grain))

hist(elev)

```

## 3.4 Exercise

```{r}
library(spData)
data(us_states)
data(us_states_df)
```


1. Create a new object called us_states_name that contains only the NAME column from the us_states object. What is the class of the new object and what makes it geographic?

```{r}

us_states_name <- us_states$NAME
class(us_states_name)


```
the new object _us_stat_name_ is character object, and it is not geographic

2. Select columns from the us_states object which contain population data. Obtain the same result using a different command (bonus: try to find three ways of obtaining the same result). Hint: try to use helper functions, such as contains or starts_with from dplyr (see ?contains).

```{r}
us_states %>%
  dplyr::select(starts_with("total_"))
  
```

3. Find all states with the following characteristics (bonus find and plot them):

- Belong to the Midwest region.
- Belong to the West region, have an area below 250,000 km2 and in 2015 a population greater than 5,000,000 residents (hint: you may need to use the function units::set_units() or as.numeric()).
- Belong to the South region, had an area larger than 150,000 km2 or a total population in 2015 larger than 7,000,000 residents.

```{r}
mid_west <- us_states %>%
  filter(REGION == "Midwest")

ggplot() +
  geom_sf(data = us_states, fill = "NA", color = "grey30") +
  geom_sf(data = mid_west, fill = "yellow", alpha = 0.8) +
  theme_map(base_family = "Open Sans") +
  labs(title = "US midwest") +
  theme(plot.title = element_text(hjust = 0.5, size = 32, margin = margin(40, 0, 0,0)))

west_region <- us_states %>%
  mutate(AREA = as.numeric(AREA)) %>%
  filter(AREA < 250000, REGION == "West", total_pop_15 > 5000000)

ggplot() +
  geom_sf(data = us_states, fill = "NA", color = "grey30") +
  geom_sf(data = west_region, fill = "yellow", alpha = 0.8) +
  theme_map(base_family = "Open Sans") +
  labs(title = "Washington State",
       subtitle = "Only state in West, which have population more than \n5 million in 2015 survey and less area than 250,000 Km^2") +
  theme(plot.title = element_text(hjust = 0.5, size = 32, margin = margin(40, 0, 0,0)),
        plot.subtitle = element_text(size = 16, face = "italic"))


```


4. What was the total population in 2015 in the us_states dataset? What was the minimum and maximum total population in 2015?

8. us_states_df has two more rows than us_states. How can you find them? (hint: try to use the dplyr::anti_join() function)

```{r}
setdiff(us_states_df$state, us_states$NAME)


```

Alaska and Hawaii not on the list. PS where is the puerto rico

14. Create a raster from scratch with nine rows and columns and a resolution of 0.5 decimal degrees (WGS84). Fill it with random numbers. Extract the values of the four corner cells.

```{r}
raster_ran <- raster(nrows = 9, ncols = 9, res = 0.5,
                     xmn = 0, ymn = 0, xmx = 4.5, ymx = 4.5,
                     vals = sample(1:81, size = 81, replace = F))
values(raster_ran)
res(raster_ran)
plot(raster_ran)

raster_ran[1,1]
raster_ran[1,9]
raster_ran[9,1]
raster_ran[9,9]

```


15. What is the most common class of our example raster grain (hint: modal())?

```{r}
grain

factorValues(grain, raster::modal(values(grain)))

```

16. Plot the histogram and the boxplot of the data(dem, package = "RQGIS") raster.

```{r}
data(dem, package = "RQGIS")

hist(dem)
boxplot(dem)

```

17. Now attach also data(ndvi, package = "RQGIS"). Create a raster stack using dem and ndvi, and make a pairs() plot.

```{r}

data(ndvi, package = "RQGIS")

s <- stack(dem, ndvi)

pairs(s)

par(mfrow = c(1, 2))
plot(s)

```



















