---
title: 'Chapter 1: Introduction'
author: "Yifei Liu"
date: "8/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Purpose of this book:

1. reading writing and manupulating geographic data
2. making static and interactive maps
3. Applying geocomputation to solve real-world problems 
4. Modeling geographic phenomena

## 1.1 What is geocomputations?


## 2.2 Why use R for gecomputation?


```{r}
library(leaflet)
popup = c("Robin", "Jakub", "Jannes")
leaflet() %>%
  addProviderTiles("Stamen.TonerLite",
                     group = "Toner") %>%
  addMarkers(lng = c(-3, 23, 11),
             lat = c(52, 53, 49), 
             popup = popup)


```

## 1.5 The history of R-spatial 


## 1.6 Exercise

1. Think about the term 'GIS', 'GDS' and 'gecomputation' describe above. Which (if any) best describes the work you would like to do use geo* mehthods and software and why?

By checking the definenation of these terms, I think I'm currently more interest in "GDS", as a social science major(Finance analysis and quantitative risk management major) I more interest in the relationship between, demographic, geographic and social measurement such as household income, net immigration. I think by incorporate geographic data will give me a new perspective. And also make chart cooler. :)
 
 2. Provide three reasons for using a scriptable language such as R for gecomputation instead of using an established GIS program such as QGIS
 
 This is easy for me, never use GIS program such as QGIS in my life, but I'm pretty familary with R langauge and graphic packages such as ggplot and leaflet.
 
 3. Name two advantanges and two disadvantage of using mature vs recent packages for geographic data analysis (for example *sp* vs *sf*)
 
 THe reason people invent new packages is because some features require the featrues that old packages don't support very well.
 
 


```{r}



```






















