---
title: "chapter 1: The Tidy Text Format"
author: "Yifei Liu"
date: "3/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=F, warning=F}
library(tidytext)
library(janeaustenr)
library(pdftools)
library(stringr)
library(tidyr)
library(gutenbergr)
library(pdftools)
library(tm)
library(tm.plugin.webmining)
library(purrr)
library(methods)
library(Matrix)
library(scales)
library(stringr)
library(reshape2)
library(ggraph)
library(widyr)
library(wordcloud)
library(widyr)
library(igraph)
library(subtools)
library(topicmodels)
library(mallet)
theme_set(theme_minimal())

detach("package:dplyr", unload=TRUE)
library(dplyr)
```


Tidy data principles is a powerful way to make handling data easier and more effective, and this is no less true when it comes to dealing with text. 

- Each variables is a column
- Each observation is a row
- Each type of observational unit is a table.

Define tidy text format as being a table with _a token per row_. 

## Constrasting Tidy Text with Other Data Structures

- String
- Cirpus
- Document-term matrix

## The unnest-tokens function


```{r}
text <- c("Because I could not stop for Death -", "He kindly stopped for me -", "The Carriage held but just Ourselves -", "and Immortality")

text_df <- tibble(line = 1:4, text = text)

text_df %>%
  unnest_tokens(word, text)

```

## Tidying the works of Jane Austen

```{r}
original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("chapter [\\divxlc]", ignore_case = T)))) %>%
  ungroup()

original_books

```


```{r}
tidy_books <- original_books %>%
  unnest_tokens(word, text)

tidy_books <- tidy_books %>%
  anti_join(stop_words)

tidy_books %>%
  count(word, sort = T) %>%
  filter(n > 600) %>%
  mutate(word = fct_reorder(word, n)) %>%
  ggplot(aes(word, n, fill = word)) +
  geom_col(fill = "midnightblue", alpha = 0.8) +
  coord_flip() +
  labs(x = "",
       y = "",
       title = "Most frequent word in Austin Book") +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.text.y = element_text(face = "italic"))


```


### The gutenbergr Package

```{r}
hgwells <- gutenberg_download(c(35, 36, 5230, 159))

tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>% 
  anti_join(stop_words)

tidy_hgwells %>%
  count(word, sort = T)

bronte <- gutenberg_download(c(1260, 768, 969, 9182, 767))

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)
```


```{r}
frequency <- bind_rows(mutate(tidy_bronte, author = "Brontë Sisters"), 
                       mutate(tidy_hgwells, author = "H.G. Wells"), 
                       mutate(tidy_books, author = "Jane Austen")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>% 
  count(author, word) %>% group_by(author) %>% 
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(author, proportion) %>% 
  gather(author, proportion, `Brontë Sisters`:`H.G. Wells`)

frequency %>%
  ggplot(aes(proportion, y = `Jane Austen`,
             color = abs(`Jane Austen` - proportion))) +
  geom_abline(color = "gray40", lty = 20) +
  geom_jitter(alpha = .1, size = 2.5, width = .3, height = .3) +
  geom_text(aes(label = word), check_overlap = T, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001),
                       low = "darkslategray4", high = "gray75") +
  facet_wrap(~ author, ncol= 2) +
  theme(legend.position = "none") +
  labs(y = "Jane Austen", x = "")

cor.test(data = frequency[frequency$author == "Brontë Sisters",],
         ~ proportion + `Jane Austen`)

cor.test(data = frequency[frequency$author == "H.G. Wells",],
         ~ proportion + `Jane Austen`)

```


