---
title: "Chapter 2"
author: "Yifei Liu"
date: "2/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2.1 Vectors

Example 2.1

```{r}
x <- matrix(c(1:3), nrow = 3)
y <- matrix(c(4:6), nrow = 3)

t(x) %*% y

```

## 2.2 Matrices


## 2.3 Matrix Arithmetic

```{r}
a <- matrix(1:4, ncol = 2, byrow = T)
b <- matrix(5:8, ncol = 2, byrow = T)

a %*% b

b %*% a

a <- matrix(c(1,1,2,2,1,3,3,1,4,4,1,5), byrow = T, ncol = 3)
b <- matrix(rep(0, 4), ncol = 1)
solve(a, b)
```

## 2.4 Transpose and trace of sums and products

If A + B is defined (i.e. A and B have the same orders) then $(A + B)' = A' + B'$ and $tr(A + B) = tr(A) + tr(B)$. If A is $m\times n$ and B is $n \times p$ then AB is $m\times n \times n\times p = m \times p$
so $(AB)'$ is $p\times m$. $(AB)'=B'A'$



## 2.5 Special Matrics

### 2.5.1 Symmetrics and skew-symmetric matrices

A square $n \times n$ matrix $A = (a_{ij})$ is *symmetric* if $\acute{A} = A$, i.e., $a_{ij} = a_{ij}$ for all i,j. 

A square matrix $B = (b_{ij})$ is *Skew-symmetric* if $\acute{B} = -B$ i.e. $b_{ij} = - b{ji}$ for all i, j. 


### 2.5.2 Product with transpose AA'

### 2.5.3 Orthogonal matrices

### 2.5.4 nromal matrices

A $p\times p$ matrix is normal if $AA' = A'A$, i.e., if A commutes with A'. Clearly all symmetric, all skew-symmetric and all orthogonal matrices are normal

### 2.5.5 Permutation matrices


```{r}
# Example 2.5
A <- matrix(1:9, 3,3, byrow = T)
E <- matrix(c(1,0,0,0,1,0), 2,3, byrow = T)
F <- matrix(c(1,0,0,1,0,0), 3,2, byrow = T)

E %*% A
A %*% F
E %*% A %*% F

```

## 2.6 Partitioned Matrices

### 2.6,1 Sub-matrtices

```{r}
# A is 
A <- matrix(c(1:9), 3, 3, byrow = T)
A
# first two row
E <- matrix(c(1, 0, 0, 0, 1,0), 2, 3, byrow = T)
E
# If you want first two rows of matrix A use this matrix to multiple A
diag(1, dim(A))[-3, ] %*% A
# last two rows
F <- t(E)
A %*% F
E %*% A %*% F 
A[1:2, 1:2]

```

### 2.6.2 Manipulation of partitioned matrices

### 2.6.3 Implementation of partitioned matrices in R

```{r}
A <- matrix(1:6, 2,3)
B <- matrix(1:6, 2,3, byrow = T)

U <- cbind(A, B)
U[1:2, 3:6]

```

## 2.7 Algebraic Manipualtion of Matrices

### 2.7.1 General expansion of products




## 2.8 Useful Tricks

### 2.8.1 Tracking dimensions annd 1* 1 matrices

### 2.8.2 Trace of products

## 2.9 Linear and quadratic forms

## 2.10 Creating Matrices in R

### 2.10.1 Ambiguidty of vectors

## 2.11 matrix Arithmetic in R

2.11.1

```{r}

A <- matrix(c(1:6), 2, 3, byrow = F)
B <- matrix(c(1:6), 2, 3, byrow = T)
C <- matrix(c(1:6), 2, 3)
D <- matrix(c(1:6), 2, 3, byrow = T)
E <- matrix(c(1:6), 3, 2, byrow = T)

A + C
A - D

```

2.11.2 Multiplication

2.11.2.1 Stand multiplicaiton

```{r}

A <- matrix(c(1:6), 2, 3, byrow = T)
B <- matrix(c(1:6), 3, 2, byrow = T)

A
A %*% B
B
B %*% A
```

2.11.2.2 Element-by-element (hadamard) multiplication

```{r}

t(B)
A * t(B)

```

2.11.2.3 Non-commuting matrices

```{r}

U <- matrix(c(1:4), 2, 2, byrow = T)
V <- matrix(c(5:8), 2, 2, byrow = T)

U

U %*% V
V %*% V
```

2.11.2.4 Commuting matrices

```{r}

W <- matrix(c(2, 2, 3, 5), 2, 2, byrow = T)

W
U %*% W
W %*% U

```

2.11.2.5 Transpose of products

```{r}

t(U %*% V)
t(V) %*% t(U)
t(U) %*% t(V)

```

so $(UV)' = V'U' \neq U'V'$

```{r}

t(U %*% W)
t(W) %*% t(U)
t(U) %*% t(W)

```

Note that U and W commute so it follows that U' and W' also commute


```{r}

U %*% t(W)
t(W) %*% U

```

But it does not follow the that because U and W commute when W' also commutes with U as the above example demonstrates

2.11.2.6 Corss-products

```{r}

A
crossprod(A)
t(A) %*% A

tcrossprod(A)
A %*% t(A)

```

2.11.2.7 Ambiguity of vectors

```{r}

X <- matrix(c(1:9), 3, 3, byrow = T)
X

a <- c(1:3)
b <- c(4:6)
a %*% X
X %*% a
b %*% X
a %*% b
b %*% a



```

Here the inner product of a and b is returned, whatever the order of the product. 

2.11.3 Diagonal matrices

2.11.3.1 Creating a diagonal matrix from a list

2.11.3.2 Extracting the diagonal

```{r}

E %*% A
diag(E %*% A)

```

2.11.3.3 Converting a matrix to diagonal

```{r}

diag(diag(E %*% A))

```

2.11.4 Trace

2.11.4.1 Trace of square matrix

```{r}

sum(diag(E %*% A))
sum(diag(U))
sum(diag(V))

```

2.11.4.2 Trace of transpose of products

```{r}

sum(diag(U))
sum(diag(t(U)))

U %*% V; V %*% U

# but

sum(diag(U%*%V)); sum(diag(U %*% V))

```

2.11.4.3 Create a fucntion for trace of a matrix



```{r}

tr <- function(x) {
  tr <- sum(diag(x))
  return(tr)
}

tr(U)

```

## 2.12 Initial statistical Application

### 2.12.2 Lienar models

### 2.12.3 Multivariate analysis

### 2.12.3.2 Sample statisic in R

```{r}

X <- t(as.matrix(A))

```








