---
title: 'Chapter 1: Introduction'
author: "Yifei Liu"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)

```



## 1.7 Examples of R commands

1.7.2 Inputting data

```{r}

A <- matrix(c(1:6), nrow = 2, ncol = 3, byrow = F)
B <- matrix(c(1:6), nrow = 2, ncol = 3, byrow = T)
A
A[1, ]

B
B[1, ]
```

```{r}

C <- matrix(c(1:6), 2, 3)
D <- matrix(c(1:6), 2, 3, byrow = T)

C
D
```


1.7.3 Calculations

```{r}

A + B
A - B
2 * A
# A %*% B

# transpose A is A'
t(A)
t(A) %*% B


```

*Beware: A \* B* gives element-by-element multiplication

```{r}

A * B

# Kronecker products
kronecker(A, B)

kronecker(B, A)

```

[The Kronecker Product of two matrices](https://www.youtube.com/watch?v=e1UJXvu8VZk)

1.7.4 Dimensions and lengths of matrices of vectros

```{r}

C <- matrix(c(1:6), 2, 3)
dim(C)
dim(t(C))
length(C)
x <- c(1:4)
length(x)
dim(x)
```

*Beware:*

```{r}
print(c(class(x), class(t(x))))
dim(x)
dim(t(x))

```

```{r}
x <- c(1, 2)
Z <- matrix(c(1:4), 2, 2)

x
Z
Z %*% x
x %*% Z

```
if *x* is foced to be a matrix, one of these multiplciations will give an error because of non-conformability

```{r}

class(x)
x <- matrix(x)
class(x)

Z %*% x
# x %*% Z
```

1.7.5 Joining matrices together

```{r}

A
C

cbind(A, C)
rbind(A, C)
t(rbind(t(A), t(B))) 
cbind(A, B)
t(cbind(t(A), t(B)))



```

17.6 Diagonals and trace

```{r}
E <- matrix(c(1:9), 3, 3, byrow = T)
E
diag(E)
diag(c(1, 5, 9))
sum(diag(E))
diag(diag(E))
```

1.7.7 Trace of products

```{r}
F <- matrix(c(1:9), 3, 3)
F
E %*% F
F %*% E


```

1.7.8 Transpose of products

```{r}

t(E %*% F)

```

1.7.9 Determinants

```{r}

G <- matrix(c(1, -2, 2, 2, 0, 1, 1, 1, -2), 3, 3, byrow = T)
G
det(G)

```

1.7.10 Diagonal matrices

```{r}

G
diag(diag(G))


```


1.7.11 Inverses

```{r}

solve(A %*% t(B))

# solve inverse by hand
A %*% t(B) 
(1 / det(A %*% t(B))) * matrix(c(64, -49, -28, 22), 2, 2, byrow = T)

# use MASS
ginv(A %*% t(B))

#solve(t(A) %*% B) computation singular

ginv(t(A) %*% B)

```

1.7.12 Eigenanalyses



```{r}

eigen(A %*% t(B))

```

[Eigen vector and values](https://www.youtube.com/watch?v=G4N8vJpf7hM)

1.7.13 Singular value decomposition

```{r}

X <- matrix(c(1:9), 3, 3, byrow = T)
X
svd(X)
```










